Probabilistic Catalogs from Crowded Star Fields

### 2012-07-10 paper/ms.tex
A small amount of writing

\title{More than one Author with different Affiliations}

@@

\title{Probabilistic Catalogs from Crowded Star Fields}
\author{Brendon J. Brewer$^{1, 2}$, David W. Hogg$^{3}$,
and Daniel Foreman-Mackey$^{3}$ \\
\\
\small
$^1$ Department of Physics, University of California, Santa Barbara,\\
\small
CA 93106, USA \\
\small
$^2$ Department of Statistics, University of Auckland,\\
\small
Private Bag 92019, Auckland, New Zealand \\
\small
$^3$ Center for Cosmology and Particle Physics, Department of Physics,
New York University,\\
\small
4 Washington Place, New York, NY, 10003, USA
}

@@

\section{Probabilistic Catalogs}
\begin{itemize}
\item Catalogs as models for what's out there \\
\item Standard techniques for constructing catalogs, and under what
cicrumstances they stop working \\
\item 
\end{itemize}

\section{The Unknown Parameters}
There are $N$ stars in the field, where $N$ is unknown. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
parameterize the {\it spatial distribution} of the stars by parameters
$\alpha$, and the distribution of fluxes (commonly known as the {\it luminosity
function}) by parameters $\beta$. In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}
The prior probability distribution for the unknown parameters can be factorized
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}
Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$, $\alpha$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the positions and fluxes of the stars come independently from
a common distribution. If we knew the spatial distribution and the luminosity
function of the stars, then the location and flux of a particular star would
not tell us anything about the location and flux of another star.

\section{Specific Models}
A model for the spatial distribution corresponds to a choice of functional
forms for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

>>>>

@@

\title{Probabilistic Catalogs from Crowded Star Fields}
\author{Brendon J. Brewer$^{1, 2, ^*}$, David W. Hogg$^{3}$,
and Daniel Foreman-Mackey$^{3}$ \\
\\
\small
$^1$ Department of Physics, University of California, Santa Barbara,\\
\small
CA 93106, USA \\
\small
$^2$ Department of Statistics, The University of Auckland,\\
\small
Private Bag 92019, Auckland 1142, New Zealand \\
\small
$^3$ Center for Cosmology and Particle Physics, Department of Physics,
New York University,\\
\small
4 Washington Place, New York, NY, 10003, USA\\
\small
$^*$\texttt{bj.brewer@auckland.ac.nz}
}

@@

A fundamental problem in astronomy is the construction of {\it catalogs} from
raw image data. Essentially, the question being answered is ``given the image
we have obtained, what objects are present in the field and what are their
properties?''.

\section{Probabilistic Catalogs}

\begin{itemize}
\item Catalogs as models for what's out there \\
\item Standard techniques for constructing catalogs, and under what
cicrumstances they stop working \\
\item 
\end{itemize}

\section{The Unknown Parameters}
Our model makes the following assumptions. There are an unknown number of stars
$N$ in the field. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
describe the {\it spatial distribution} of the stars by parameters
$\alpha$, and the distribution of fluxes (commonly known as the {\it luminosity
function}) by parameters $\beta$. In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}
The prior probability distribution for the unknown parameters can be factorized
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}
Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$, $\alpha$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the positions and fluxes of the stars come independently from
a common distribution. If we knew the spatial distribution and the luminosity
function of the stars, then the location and flux of a particular star would
not tell us anything about the location and flux of another star.

\section{Simulated Data}

A model for the spatial distribution corresponds to a choice of functional
forms for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:
